Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2023-11-22 Text/Articles/MIGARS_2024/The Entropy as a Proxy for Fully Developed Speckle.Rmd
Caption of Fig. 2

```{r 3d_GIO, fig.align="center",  out.width = "70%", fig.cap="Simulation of entropy for ${G}_I^0$. ", fig.show="hold",  fig.pos="hbt"}
knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf")
```
As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the Entropy of the $G_I^0$ distribution. 
We can identify regions where Entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space.

>>>>

```{r 3d_GIO, fig.align="center",  out.width = "70%", fig.cap="The Shannon Entropy under ${G}_I^0$ models.", fig.show="hold",  fig.pos="hbt"}
knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf")
```
As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the Entropy of the $G_I^0$ distribution. 
We can identify regions where Entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space.
